\cvsection{Experience}

\begin{cventries}
  \cventry
    {Research Assistant} % Job title
    {\href{https://www.inesctec.pt/en}{INESC-TEC \faExternalLink}} % Organization
    {Porto, Portugal} % Location
    {July 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Currently developing a distributed application for P2P energy trading in microgrids, taking into account the grid's maximum flow capacity.}
        \item {Planned, designed and implemented the system in an Ethereum blockchain, programming smart contracts in Solidity and testing them with Truffle Suite.}
        \item {Developed swift economic clearing algorithms using Python and GraphQL.}
        \item {Built a fluid exchange-style web app using React/Redux (emphasis on Hooks). Hosted on a Google Cloud VPS with Nginx.}
      \end{cvitems}
    }

    \cventry
    {Teaching Assistant} % Job title
    {\href{https://sigarra.up.pt/feup/en/ucurr_geral.ficha_uc_view?pv_ocorrencia_id=459473}{Faculty of Engineering of the University of Porto \faExternalLink}} % Organization
    {Porto, Portugal} % Location
    {October 2020 - January 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assisted the teacher during the practical classes of LCOM - Computer Laboratory at FEUP.}
        \item {Helped the students regarding programming in C and developing low level software and embedded software for computer peripherals.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {\href{https://www.criticalsoftware.com/en}{Critical Software \faExternalLink}} % Organization
    {Coimbra, Portugal} % Location
    {July 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learned about the methodologies and tools used in designing robust distributed systems for critical projects, such as software for airplanes, trains and banks.}
        \item {Built a real time chat service using Java and Kafka.}
        \item {Built an automatic encryption/decryption system for smart meter data with Java, SSL and XML documents.}
      \end{cvitems}
    }

  \cventry
    {Engineer Intern} % Job title
    {IKEA Industry Portugal} % Organization
    {Paços de Ferreira, Portugal} % Location
    {June 2019 - August 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Planned and thoroughly studied the implementation of a computer vision system reinforced with machine learning to detect missing components on packaging lines, reducing their occurence by up to a predicted 95\%.}
        \item {Developed testing scripts using Python and open source computer vision libraries like OpenCV.}
      \end{cvitems}
    }
   
\end{cventries}
