\cvsection{Projects}

\begin{cventries}

  \cventry
    {} % Empty position
    {\href{https://github.com/softeng-feup/open-cx}{OpenCX}} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Developed an open source mobile app that provides swift navigation between key spots in a conference, through the use of an interactive map.}
		    \item {Development using Flutter, Redux, SQLite, Google Maps' API and GPS technology.}
      \end{cvitems}
    }

    \cventry
    {} % Empty position
    {\href{https://github.com/MiguelDelPinto/LCOM_TPs}{Space Lander}} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {A videgame inspired from the famous Lunar Lander, where a player must land its scaceship safely, avoiding asteroids and rocky terrains.}
      	\item {Programmed the PC's peripherals (graphics gard, keyboard, mouse, timer, RTC and serial port), developing low level drivers and embedded software and adopting an event driven methodology and an object oriented approach.}
		    \item {Fully developed using C and used SVN for version control.}
      \end{cvitems}
    } 

    \cventry
    {} % Empty position
    {\href{https://github.com/MiguelDelPinto/PLOG_Proj/tree/master/AztecMath}{Aztec Math Puzzle Solver}} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed an efficient solver for Aztec Math puzzles using Prolog and constraint logic programming.}
		    \item {Currently writing a scientific article to be published in EPIA 2020 - Lisbon.}
      \end{cvitems}
    }


  \cventry
    {} % Empty position
    {School Rides} % Project
    {} % Empty location
    {} % Empty date
    {
      \begin{cvitems} % Description(s) bullet points
      	\item {Program that calculates optimal paths for school buses, when picking up students from their homes.}
		    \item {Used advanced graph algorithms and heuristics to improve efficiency and calculation speed when dealing with NP-complete problems.}
		    \item {Developed using C++ and GraphViewer (Java API).}
      \end{cvitems}
    }

   
\end{cventries}